%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page One Column Resume
% LaTeX Template
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{rinkal_resume}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rinkal}{Agrawal}{ \href{mailto:agrawa55114l.rinkal.us@gmail.com}{agrawal.rinkal.us@gmail.com} \thinspace
| \thinspace St.Paul, MN \thinspace
| \thinspace +1 612.532.7639 \thinspace
| \thinspace
\faGithubAlt \thinspace \thinspace 
\faLinkedin \thinspace \thinspace 
\faMedium \thinspace : {/agrawalrinkal}
}

\small

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Software Engineer ii} | CenturyLink\hfill\  \location{Nov '18 – Present} 
\location{Software Engineer I | CenturyLink\hfill June '17 - Nov '18}
\vspace{2pt}
\begin{tightemize}
\item Received \custombold{40\% fewer error tickets} by developing a data-driven application using Angular6 on node.js and Java to provide a user interface for multiple inventories. 
\item \custombold{Reduced} device activation time from \custombold{30+ minutes to just over 4 minutes} by streamlining an automation solution in Java for SD-WAN technology, by closely working with different business units.
\item \custombold{Decreased 20\% client load} by building a routing engine using JavaScript and JSON on express.js to redirect request specific incoming traffic.
\item \custombold{Revamped the legacy app efficiency by 4 folds}, by rewriting the algorithm using SNMP technology and batching, \custombold{saving almost \$100K annually}.
\item \custombold{Led multiple projects}, directed features, worked with users to gather requirements and feedback, presented demos, and facilitated communication. Executed continuous releases to ensure business requirements are being met.
\end{tightemize}
\sectionsep

\runsubsection{Software Developer Intern} | Design Ready Controls Inc. \hfill \location{June '16 – June '17}
\vspace{2pt}
\begin{tightemize}
\vspace{1pt}
\item \custombold{Increased design delivery efficiency by 30\%}, by adding multiple cutting-edge features using C\# and .Net that helped electrical engineers better understand and faster design the customized control panels.
\item \custombold{Redesigned the UI for the iOS app} that let users visualize the field sensors data in real time using AWS.
\end{tightemize}
\smallsectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Undergrad Researcher} | U of M Software Engineering Center \hfill \location{Aug '16 – Dec '16}
\vspace{2pt}
\begin{tightemize}
\item Researched on a \custombold{NASA project} under Prof. Sanjai Rayadurgam to display \custombold{autonomous applications of quadcopter drone}.
\item Achieved the autonomous application by installing a tweaked NASA octocopter software on a pixhawk hardware.
\end{tightemize}
\smallsectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Xylophone} \location{ | Independent, 3 weeks  \hfill | Swift, Xcode}
\vspace{2pt}
\begin{tightemize}
\item Designed a sleek looking iOS app to \custombold{imitate a real life xylophone} with 7 bars playing different tones.
\item Added a feature to record and save played tunes.
\end{tightemize}
\sectionsep

\runsubsection{Speech Converter} \location{ | Independent, 1 week  \hfill | JavaScript, HTML}
\vspace{2pt}
\begin{tightemize}
\item Developed a user interface to convert voice speech to text \custombold{in real-time using Google Cloud API's}.
\end{tightemize}
\sectionsep

\runsubsection{Sentiment Analyzer} \location{ | Independent, 3 weeks  \hfill | Python, PyTorch}
\vspace{2pt}
\begin{tightemize}
\item Built the model to predicted positive or negative user sentiment given the text in English language.
\item Used \custombold{RNN and LSTM (Long Short Term Memory)} to analyze the text by giving importance to the word sequence \& \custombold{trained the model on over 25K IMDB reviews}. 
\end{tightemize}
\sectionsep

\runsubsection{Style Transfer} \location{ | Independent, 2 weeks  \hfill | Python, PyTorch}
\vspace{2pt}
\begin{tightemize}
\item Devised a \custombold{Convolutional Neural Network} using a \custombold{pre-trained VGG19 model} to transfer the style of one image onto the content of another image.
\item Built a model to extract content and style features form images and later used losses to achieve the desired target image.
\end{tightemize}
\sectionsep

\runsubsection{Envoy} \location{ | Independent, 13 weeks, team of 4  \hfill | React, Java}
\vspace{2pt}
\begin{tightemize}
\item Aimed to conduct instructor-led online classes \custombold{for hearing impaired students} through video messaging channels to help improve the university experience. Used beta to \custombold{organize 3 classes with 20+ students} in each class.
\item Collaborated with hearing-impaired students to understand their problems and collect requirements.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\runsubsection{B.S. in Computer Science \quad |} \descript{University of Minnesota- Twin Cities}
\small \custombold{May 2017  Graduate | CGPA: 3.64/4.0} | Dean's List recipient for all semesters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Exposure}
\boldHeading{Languages:} % \quad \quad \quad \hspace{4mm}}
\custombold{Swift} \textbullet{} 
\custombold{Java} \textbullet{} 
\custombold{Python} \textbullet{} 
C++ \textbullet{} 
Typescript \textbullet{} 
C \textbullet{} 
JavaScript \textbullet{} 
C\# \textbullet{} 
HTML5 \textbullet{} 
CSS3 \textbullet{} 
MySQL 

\boldHeading{Frameworks:} % \quad \quad  \quad \hspace{2mm}}
\custombold{Xcode} \textbullet{} 
\custombold{Angular} \textbullet{} 
\custombold{Node.js} \textbullet{} 
\custombold{PyTorch} \textbullet{} 
Express.js \textbullet{} 
MongoDB \textbullet{} 
React \textbullet{} 
.Net \textbullet{} 
Bootstrap 

\boldHeading{Strong Knowledge:} % \hspace{2mm}}
\custombold{Product Ownership} \textbullet{} 
\custombold{RESTful Services} \textbullet{} 
Micro services Architecture \textbullet{} 
Git \textbullet{} 
Agile Methodology \textbullet{}

\newlength\boxwid
\settowidth{\boxwid}{\indent\hspace{0.5cm}}
\hspace{3.25cm} \hangindent=\boxwid 
Multi-threading \textbullet{} 
Unit Testing \textbullet{} 
Tomcat \textbullet{} 
Apache 

\boldHeading{Working Knowledge:}
\custombold{Neural Networks(MLP, CNN, RNN, LSTM)}  \textbullet{} 
Redis \textbullet{} 
Flask \textbullet{} 
RabbitMQ \textbullet{}  
AWS \textbullet{} 
Zookeeper \textbullet{} 
MVC 
\smallsectionsep

\end{document}  \documentclass[]{article}
